Patient movements

### 2024-05-21 analysis/patient-tracking.Rmd
Examples person movements manuscript

```{r}
# spatial track counts
tracking_data <- do.call(
  rbind,
  lapply(
    list.files("data-raw/patient-tracking/annotated",
      full.names = TRUE
    ),
    readRDS
  )
) %>%
  rename(date_time = time) %>%
  mutate(date = as.Date(date_time)) %>%
  filter(date %in% tracking_dates) %>%
  filter(between(hour(date_time), 8, 15)) %>%
  mutate(
    room = ifelse(is_waitingroom, "Waiting room",
      ifelse(is_tbroom, "TB room",
        ifelse(is_passage, "Corridor", NA)
      )
    ),
    room = factor(room, levels = c("Waiting room", "Corridor", "TB room"))
  )

@@

```{r}
# unique id
df$day_pid <- paste(df$date, df$patient_id)

@@

# manual sample of tracks
ex_pid_man <- c(
  "2021-10-25 4649", # Entered + Exited, including TB room stay
  "2021-10-13 6297", # Lost Exit, only waiting room
  "2021-11-04 12860", # (Entered) + Exited, waiting room and corridor
  "2021-10-13 9346", # Entered + Exited, including TB room
  "2021-11-05 16625", # Entered + (Exited), only waiting room
  "2021-10-25 9526", # Lost Exit, waiting room and corridor
  "2021-11-04 9841", # Entered = (Exited), waiting room and corridor
  "2021-10-15 8644", # Entered + Exited, including TB room
  "2021-10-15 9419" # Lost Enter
)
ex_df_man <- df %>% filter(day_pid %in% ex_pid_man)
ex_df_man_se <- ex_df_man %>%
  group_by(day_pid) %>%
  slice(1, n()) %>%
  mutate(type = factor(c("Start", "End"), levels = c("Start", "End"))) %>%
  ungroup()

# plot
ex_tracks <- plot_spatial(
  ggplot() +
    geom_path(
      data = ex_df_man,
      mapping = aes(x = x, y = y),
      color = "darkred"
    ) +
    geom_point(
      data = ex_df_man_se,
      mapping = aes(x = x, y = y, shape = type),
      size = 2
    ) +
    facet_wrap(~day_pid, ncol = 3) +
    scale_shape_manual(values = c(1, 13)),
  text_descr = 8
) +
  theme(
    legend.position = "none"
  )

>>>>

```{r}
tracking_dates <- c(
  "2021-10-13", "2021-10-15", "2021-10-25", "2021-11-04", "2021-11-05"
)

# spatial track counts
tracking_data <- do.call(
  rbind,
  lapply(
    list.files("data-raw/patient-tracking/annotated",
      full.names = TRUE
    ),
    readRDS
  )
) %>%
  rename(date_time = time) %>%
  mutate(date = as.Date(date_time)) %>%
  filter(date %in% tracking_dates) %>%
  filter(between(hour(date_time), 8, 15)) %>%
  mutate(
    room = ifelse(is_waitingroom, "Waiting room",
      ifelse(is_tbroom, "TB room",
        ifelse(is_passage, "Corridor", NA)
      )
    ),
    room = factor(room, levels = c("Waiting room", "Corridor", "TB room"))
  )

@@

```{r}
# unique id
df$day_pid <- paste("Date:", df$date, " |  ID:", df$patient_id)

@@

# manual sample of tracks
ex_pid_man <- c(
  "Date: 2021-10-25  |  ID: 4649", # Entered + Exited, including TB room stay
  # "2021-10-13 6297", # Lost Exit, only waiting room
  # "2021-11-04 12860", # (Entered) + Exited, waiting room and corridor
  # "2021-10-13 9346", # Entered + Exited, including TB room
  # "2021-11-05 16625", # Entered + (Exited), only waiting room
  "Date: 2021-10-25  |  ID: 9526", # Lost Exit, waiting room and corridor
  "Date: 2021-11-04  |  ID: 9841", # Entered = (Exited), waiting room and corridor
  "Date: 2021-10-15  |  ID: 8644" # Entered + Exited, including TB room
  # "2021-10-15 9419" # Lost Enter
)
ex_df_man <- df %>% filter(day_pid %in% ex_pid_man)
ex_df_man_se <- ex_df_man %>%
  group_by(day_pid) %>%
  slice(1, n()) %>%
  mutate(type = factor(c("Start", "End"), levels = c("Start", "End"))) %>%
  ungroup()

# plot
ex_tracks <- plot_spatial(
  ggplot() +
    geom_path(
      data = ex_df_man,
      mapping = aes(x = x, y = y),
      color = "darkred"
    ) +
    geom_point(
      data = ex_df_man_se,
      mapping = aes(x = x, y = y, shape = type),
      size = 2
    ) +
    facet_wrap(~day_pid, ncol = 2) +
    scale_shape_manual(values = c(1, 13)),
  text_descr = 8
) +
  theme(
    legend.position = "none"
  )
